results notes

### 2022-09-01 RR_manuscript/results_notes.Rmd
name unnamed chunks

```{r}

@@

## Acoustic analysis 
`r round(outcome_n[[1,1]],2) * 100`\% of models used a duration measure as the outcome variable, `r round(outcome_n[[2,1]],2) * 100`\% used a f0 measure, `r round(outcome_n[[3,1]],2) * 100`\% used a formant measure, `r round(outcome_n[[4,1]],2) * 100`\% used an intensity measure, and `r round(outcome_n[[5,1]],2) * 100`\% used a different measure.

@@

# Meta analysis
```{r}

@@

# Discussion drafty
## Summary
We gave XX analyst teams the same acoustic dataset to answer the same research question. 
In order to answer the question, teams had to operationalize latent variables within a multidimensional signal, operationalize and chose appropriate predictors, and construct an appropriate statistical model to answer the research question. 
This complex process led to a large garden of forking paths.  
Each individual analyst team chose unique paths to acoustically measure, operationalize and statistical analyse the data.
Interestingly, the observed variation in reported effect sizes was not predicted by the analysts' prior expectations about the phenomenon.
In fact, teams on average rated the plausibility of the effect as rather high before receiving access to the data.
The variation in reported effect sizes was neither predicted by the analysts' experience in the field nor by the perceived quality of the analysis as judged by other teams. 
Analyses received overall high peer ratings for both the acoustic and the statistical analysis, suggesting that reviewers were generally satisfied with the other teams' approaches.
These findings are very much in line with previous crowd-sourced projects that suggested variation between teams is neither driven by perceived quality of the analysis nor by analysts biases or experience (REF,REF,REF). 
Given the mounting evidence, Breznau et al. (2021) concluded that "[...] we are left to believe that idiosyncratic uncertainty is a fundamental feature of the scientific process that is not easily explained by typically observed researcher characteristics or analytical decisions." 
Idiosyncratic variation across researchers might be a fact of life which researchers have to acknowledge and integrate into how they evaluate and present evidence.

>>>>

```{r, 'load-data'}

@@

## Acoustic analysis

`r round(outcome_n[[1,1]],2) * 100`\% of models used a duration measure as the outcome variable, `r round(outcome_n[[2,1]],2) * 100`\% used a f0 measure, `r round(outcome_n[[3,1]],2) * 100`\% used a formant measure, `r round(outcome_n[[4,1]],2) * 100`\% used an intensity measure, and `r round(outcome_n[[5,1]],2) * 100`\% used a different measure.

@@

# Meta analysis

```{r, 'load-meta-analysis'}

@@

# Discussion drafty

## Summary

We gave XX analyst teams the same acoustic dataset to answer the same research question. 
In order to answer the question, teams had to operationalize latent variables within a multidimensional signal, operationalize and chose appropriate predictors, and construct an appropriate statistical model to answer the research question. 
This complex process led to a large garden of forking paths.  
Each individual analyst team chose unique paths to acoustically measure, operationalize and statistical analyse the data.
Interestingly, the observed variation in reported effect sizes was not predicted by the analysts' prior expectations about the phenomenon.
In fact, teams on average rated the plausibility of the effect as rather high before receiving access to the data.
The variation in reported effect sizes was neither predicted by the analysts' experience in the field nor by the perceived quality of the analysis as judged by other teams. 
Analyses received overall high peer ratings for both the acoustic and the statistical analysis, suggesting that reviewers were generally satisfied with the other teams' approaches.
These findings are very much in line with previous crowd-sourced projects that suggested variation between teams is neither driven by perceived quality of the analysis nor by analysts biases or experience (REF,REF,REF). 
Given the mounting evidence, Breznau et al. (2021) concluded that "[...] we are left to believe that idiosyncratic uncertainty is a fundamental feature of the scientific process that is not easily explained by typically observed researcher characteristics or analytical decisions." 
Idiosyncratic variation across researchers might be a fact of life which researchers have to acknowledge and integrate into how they evaluate and present evidence.
